\newpage
\renewcommand{\refname}{Tài liệu tham khảo}
\renewcommand{\bibname}{Tài liệu tham khảo}

\begin{thebibliography}{99}

\bibitem{freertos-doc}
FreeRTOS. \textit{FreeRTOS Kernel Documentation}. Available: \url{https://www.freertos.org/Documentation/RTOS_book.html}

\bibitem{espressif-idf}
Espressif Systems. \textit{ESP-IDF Programming Guide (ESP32-S3)}. Available: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32s3/}

\bibitem{arduino-esp32}
Espressif Systems. \textit{Arduino-ESP32 Documentation}. Available: \url{https://docs.espressif.com/projects/arduino-esp32/en/latest/}

\bibitem{platformio}
PlatformIO. \textit{PlatformIO Documentation}. Available: \url{https://docs.platformio.org/}

\bibitem{dht20-datasheet}
ASAIR. \textit{DHT20 Temperature and Humidity Sensor Datasheet}. Available: \url{https://www.aosong.com/en/products-40.html}

\bibitem{liquidcrystal-i2c}
Arduino Community Libraries. \textit{LiquidCrystal I2C Library}. Available: \url{https://github.com/johnrickman/LiquidCrystal_I2C}

\bibitem{neopixel-lib}
Adafruit. \textit{Adafruit NeoPixel Library}. Available: \url{https://github.com/adafruit/Adafruit_NeoPixel}

\bibitem{async-webserver}
ESPAsyncWebServer Contributors. \textit{ESPAsyncWebServer}. Available: \url{https://github.com/ESP32Async/ESPAsyncWebServer}

\bibitem{arduinojson}
Benoit Blanchon. \textit{ArduinoJson Documentation}. Available: \url{https://arduinojson.org/}

\bibitem{pubsubclient}
Nick O'Leary. \textit{PubSubClient: MQTT Library for Arduino}. Available: \url{https://pubsubclient.knolleary.net/}

\bibitem{mqtt-spec}
OASIS. \textit{MQTT Version 3.1.1}. Available: \url{https://docs.oasis-open.org/mqtt/mqtt/v3.1.1/mqtt-v3.1.1.html}

\bibitem{mosquitto-doc}
Eclipse Foundation. \textit{Eclipse Mosquitto Documentation}. Available: \url{https://mosquitto.org/documentation/}

\bibitem{tflm}
TensorFlow. \textit{TensorFlow Lite for Microcontrollers}. Available: \url{https://www.tensorflow.org/lite/microcontrollers}

\end{thebibliography}
